Online Laterality Battery Pre-Processing - short version

### 2020-02-12 battery-preprocessing_v3_DB.Rmd
Based t-test on log RT rather than raw RT

  nsubs <- nrow(demographics)
  demographics$tlat_RDT<-NA
   demographics$plat_RDT<-NA
  for (i in 1:nsubs) {
    w<-which(myfile$subject==demographics$subject[i])
    if(length(w)>0)
    {
      myt<-t.test(myfile$RT[w]~myfile$side[w])
      demographics$tlat_RDT[i]<-myt$statistic
      demographics$plat_RDT[i]<-myt$p.value
    }
  }
   if (d==1){
     maxcol <-length(colnames(demographics))
     colnames(demographics)[(maxcol-1):maxcol]<-c('tlat_RDT_1','plat_RDT_1')
   }
   if (d==2){
     maxcol <-length(colnames(demographics))
     colnames(demographics)[(maxcol-1):maxcol]<-c('tlat_RDT_2','plat_RDT_2')
   }
}
colcount<-length(colnames(demographics))
# Remove values for cases that are excluded for low acc: do this for both times by just blitzing last 4 columns of demographics
w<-which(is.na(demographics$Day1.RDT_RT_LI))
demographics[w,(colcount-3):colcount]<-NA
w<-which(is.na(demographics$Day2.RDT_RT_LI))
demographics[w,(colcount-3):colcount]<-NA

>>>>

  nsubs <- nrow(demographics)
  demographics$tlat_RDT<-NA
   demographics$plat_RDT<-NA
  for (i in 1:nsubs) {
    w<-which(myfile$subject==demographics$subject[i])
    if(length(w)>0)
    {
      myt<-t.test(log(myfile$RT[w])~myfile$side[w])  #NB USING LOG HERE TO GIVE MORE NORMAL RT DATA
      demographics$tlat_RDT[i]<-myt$statistic
      demographics$plat_RDT[i]<-myt$p.value
    }
  }
   if (d==1){
     maxcol <-length(colnames(demographics))
     colnames(demographics)[(maxcol-1):maxcol]<-c('tlat_RDT_1','plat_RDT_1')
   }
   if (d==2){
     maxcol <-length(colnames(demographics))
     colnames(demographics)[(maxcol-1):maxcol]<-c('tlat_RDT_2','plat_RDT_2')
   }
}
colcount<-length(colnames(demographics))
# Remove values for cases that are excluded for low acc: do this for both times by just blitzing last 4 columns of demographics
w<-which(is.na(demographics$Day1.RDT_RT_LI))
demographics[w,(colcount-3):colcount]<-NA
w<-which(is.na(demographics$Day2.RDT_RT_LI))
demographics[w,(colcount-3):colcount]<-NA
